Choosing a space occupancy metric

### 2024-06-04 Analysis/Choosing_metrics_vignette.Rmd
Update Choosing_metrics_vignette.Rmd

```{r, fig.height = 8, fig.width = 4}
par(mfrow = c(1, 2))
plot(rarefied_conv_vol, main = "raw data")
plot(rarefied_conv_vol, rarefaction = 37, main = "rarefied data")
```

>>>>

```{r, fig.height = 4, fig.width = 8}
par(mfrow = c(1, 2))
plot(rarefied_conv_vol, main = "raw data")
plot(rarefied_conv_vol, rarefaction = 37, main = "rarefied data")
```
